Dark matter halo shape in the Auriga simulations: radial dependence, time evolution and correlation with baryon disk properties

### 2019-07-17 Document/paper.tex
caption figure 1

\begin{figure*}
  \centering
  \subfloat[DM shape at small radius]{\includegraphics[width=0.5\textwidth]{level4_DM_halo_24_2.png}} 
  \hfill
  \subfloat[DM shape at large radius]{\includegraphics[width=0.5\textwidth]{level4_DM_halo_24_4.png}} 
  \hfill

  \subfloat[MHD shape at small radius]{\includegraphics[width=0.5\textwidth]{level4_MHD_halo_24_2.png}} 
  \hfill
  \subfloat[MHD shape at large radius]{\includegraphics[width=0.5\textwidth]{level4_MHD_halo_24_4.png}} 
  \hfill 
  \caption{DM density in a slice with width one tenth of the virial radius.
  The black ellipses show the result of the fitting procedure. 
  Upper panels correspond to DM only simulations, lower panels to MHD simulations.
  Left panels show data at small radii, while right panels at large
  radii.
  The cut is made along the minor axis of the halo shape.}
\label{fig:slices}
\end{figure*}

>>>>

\begin{figure*}
  \centering
  \subfloat[DMO simulation. Shape at small radius.]{\includegraphics[width=0.5\textwidth]{level4_DM_halo_24_2.png}} 
  \hfill
  \subfloat[DMO simulation. Shape at large radius.]{\includegraphics[width=0.5\textwidth]{level4_DM_halo_24_4.png}} 
  \hfill

  \subfloat[MHD simulation. Shape at small radius.]{\includegraphics[width=0.5\textwidth]{level4_MHD_halo_24_2.png}} 
  \hfill
  \subfloat[MHD simulation. Shape at large radius.]{\includegraphics[width=0.5\textwidth]{level4_MHD_halo_24_4.png}} 
  \hfill 
  \caption{DM density in logarithmic scale within a slice of one tenth
    of the virial radius in width. 
    The cut is perpendicular to the short axis of the inertia tensor ellipsoid.
    The black ellipses show the results of the fitting procedure. 
    Upper panels correspond to DMO simulations, lower panels to MHD
    simulations.
    All cases correspond to \texttt{Level4} resolution.
    Left panels show data at small radii, while right panels at large
    radii.    
    This halo showcases the most noticeable effect in all halos
    across the Auriga simulations: DM halos are rounder at all radii
    after baryonic physics is included.}
\label{fig:slices}
\end{figure*}
